%-------------------------
% Cover Letter - Airbnb iOS New Grad
% Author: Ajay Venkatesh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 30, 2026

\vspace{6pt}

Hiring Manager \\
Airbnb

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh --- wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) with roughly four years of production software experience: three at PwC in Bengaluru, a summer SDE internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. My focus has been on backend, frontend, and mobile-targeted full-stack systems.

The Airbnb posting hits a few of my strongest threads. At Amazon I built a \textbf{React 18 frontend} with optimized API integration, advanced filtering, and client-side caching that cut page load time \textbf{40\%} --- a lot of that work translated cleanly to mobile thinking (async networking, caching strategies, REST API design). At NYU I architected an \textbf{NSF-funded (\$100K)} health platform shipped to \textbf{iOS and Android} with real-time wearable telemetry, cloud-hosted ML models, and async processing pipelines. Most of my native code has been Java and TypeScript so far, so I'm honest that I've got Swift to grow into --- but my CS fundamentals (data structures, algorithms, design patterns, systems thinking) are deep, and I've shipped enough across stacks to learn fast.

What pulled me toward Airbnb is the product itself. Apps people open at moments that matter --- planning a trip, hosting strangers, finding somewhere to belong --- have a different kind of weight than generic SaaS surfaces. The iOS code I'd write here is what someone actually touches before flying somewhere new, and that's the kind of stake I want on my work.

One quick note on the AI shift. I came up pre-AI --- bachelor's and PwC were core engineering: system design, data modeling, reliable backends under load. Then ML, deep learning, and RAG through coursework. These days I use Cursor and GitHub Copilot daily, but I still verify trade-offs and understand the system before shipping production code. Strong fundamentals plus modern AI tools, not one or the other.

I'd love the chance to bring that mix to Airbnb's iOS team and grow into Swift on a team that ships at this scale. Thanks for considering my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
