%-------------------------
% Cover Letter - Qualcomm
% Author: Ajay Venkatesh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 25, 2026

\vspace{6pt}

Hiring Manager \\
Qualcomm

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh --- wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) with roughly four years of production software experience: three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. My focus has been \textbf{Python} and \textbf{Java/C++} backends, AI/LLM systems, and computer architecture.

The Qualcomm posting hits a few of my strongest threads. I work daily in Python, built distributed \textbf{Java} backends at Amazon, and use \textbf{C++} for systems-level work; on the AI side, I've shipped LLM \textbf{RAG} pipelines and Hugging Face transformer models in \textbf{PyTorch}. Most relevant: my \textbf{RV32I (RISC-V) processor simulator} with 5-stage pipelined cores --- hazard detection, EX/MEM-to-EX forwarding, load-use stalls --- gave me hands-on grounding in the pipelined dataflow concepts behind edge AI inference.

What pulled me toward Qualcomm is the on-device AI angle. Pushing generative models to the connected edge --- phones, vehicles, IoT --- is one of the harder bets in AI right now, and the kind of low-level systems-meets-models work I want to grow in.

On the AI shift: I came up pre-AI --- bachelor's and PwC were core engineering (system design, data modeling, reliable backends). Then ML, deep learning, and computer architecture through coursework. These days I use Cursor and Copilot daily, but I still verify trade-offs before shipping. Fundamentals plus AI, not either alone.

I'd love to bring that mix to Qualcomm's AI Stack team. Thanks for considering my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
