%-------------------------
% Cover Letter - Aurora
% Author: Ajay Venkatesh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 25, 2026

\vspace{6pt}

Hiring Manager \\
Aurora Innovation

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh. I'm wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) and have roughly four years of production software experience --- three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. Most of that time has been on \textbf{TypeScript and React} frontends, Python/Java backends, and AWS infrastructure.

The Visualization role lines up well with work I've actually shipped. At Amazon, I built a \textbf{React 18 frontend} with optimized API integration, advanced filtering, and client-side caching that cut page load time by 40\%. At NYU, I shipped a full-stack analytics product in React, Node.js, and REST APIs, and built \textbf{computer vision pipelines} (YOLOv8, EfficientNet) for image-based workflows. And on the visual storytelling side, my Flight Delay Prediction project surfaced feature importance and delay distributions through Seaborn, Matplotlib, and Plotly --- adjacent to the kind of data-heavy visualization your team builds for autonomy engineers.

What pulled me toward Aurora is the mission. Self-driving freight isn't a SaaS UI problem --- every visualization choice your team makes feeds engineers who decide whether the truck behaves safely. That kind of weight on the work is what I want to build toward.

One quick note on the AI shift. I came up pre-AI --- my bachelor's and PwC years were all core engineering: system design, data modeling, reliable backends under real load. Then I went deeper through coursework in ML, deep learning, big data, and RAG. These days I use Cursor and GitHub Copilot daily, but I still verify trade-offs and understand the system before shipping production code. Strong fundamentals plus modern AI tools, not one or the other.

I'd love the chance to bring that mix to Aurora's Visualization team and help shape the tools your autonomy engineers rely on. Thanks for taking the time to consider my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
