%-------------------------
% Cover Letter - Just Appraised
% Author: Ajay Venkatesh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 24, 2026

\vspace{6pt}

Hiring Manager \\
Just Appraised

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh. I'm wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) and have roughly four years of production software experience --- three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. Most of that time has gone into Python backends, LLM/RAG systems, and cloud infrastructure on AWS.

The Just Appraised posting reads like a tour of work I've actually shipped. At Amazon I built a \textbf{RAG pipeline} with an agentic workflow and a \textbf{Model Context Protocol server} for tool-augmented retrieval, cutting Athena query cost and latency by 40\%. At Campus Mesh I own CampusIQ end-to-end --- prompt engineering, chunking, embedding indexing, and grounded retrieval over Python services on PostgreSQL. And at PwC I spent three years on an \textbf{NLP/OCR pipeline} using LayoutLM that replaced manual document data entry, which is exactly the problem space you're tackling for local governments.

What pulled me toward Just Appraised is the impact. Replacing manual data entry inside the agencies that fund schools, roads, and public services is one of the rare AI products where the stakes feel concrete --- the kind of work I want to spend my time on.

One quick note on the AI shift. I came up pre-AI --- my bachelor's and PwC years were all core engineering: system design, data modeling, reliable backends under real load. Then I went deeper through coursework in ML, deep learning, big data, and RAG. These days I use Cursor and Claude Code daily, but I still verify trade-offs and understand the system before shipping production code. Strong fundamentals plus modern AI tools, not one or the other.

I'd welcome the chance to bring that mix to your conversation engine and RAG infrastructure. Thanks for taking the time to consider my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
