%-------------------------
% Cover Letter - SambaNova Systems
% Author: Ajay Venkatesh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 25, 2026

\vspace{6pt}

Hiring Manager \\
SambaNova Systems

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh. I'm wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) and have roughly four years of production software experience --- three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. Most of that time has gone into \textbf{Python} backends, LLM/inference systems, and cloud infrastructure on AWS.

The SambaStack role lines up well with work I've shipped. At Amazon I built a \textbf{RAG pipeline} plus a \textbf{Model Context Protocol server} that cut LLM inference cost and latency by 40\% on auto-scaling \textbf{Kubernetes-style ECS clusters} --- AI infrastructure at the heart of an inference serving stack. At PwC I designed a distributed Azure backend supporting \textbf{ML inference pipelines} with event-driven processing and strong API contracts. Across all roles I've leaned heavily on \textbf{unit and integration testing} with Mockito and Python frameworks, and on the side, my RV32I processor simulator project gave me hands-on understanding of pipelined hardware --- useful context for a chip-to-model platform like yours.

What pulled me toward SambaNova is the chip-to-model angle. Co-designing the \textbf{RDU silicon} with the inference stack is a rare problem space, and helping enterprises run their own foundation models on dedicated hardware feels like one of the more interesting bets in AI right now.

One quick note on the AI shift. I came up pre-AI --- bachelor's and PwC were core engineering: system design, data modeling, reliable backends under real load. Then I went deeper through coursework in ML, deep learning, big data, and RAG. These days I use Cursor and GitHub Copilot daily, but I still verify trade-offs and understand the system before shipping production code. Strong fundamentals plus modern AI tools, not one or the other.

I'd welcome the chance to bring that mix to the SambaStack team and help shape your inference serving platform. Thanks for taking the time to consider my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
