%-------------------------
% Cover Letter - SeatGeek New Grad
% Author: Ajay Venkatesh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 30, 2026

\vspace{6pt}

Hiring Manager \\
SeatGeek

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh --- wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) with roughly four years of production software experience: three at PwC in Bengaluru, a summer SDE internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. My focus has been on \textbf{Python} and \textbf{TypeScript} backends, \textbf{React} frontends, and cloud infrastructure on AWS.

The SeatGeek posting hits a few of my strongest threads. At Amazon I built a \textbf{React 18 frontend} with optimized API integration, advanced filtering, and client-side caching that cut page load time \textbf{40\%}. At NYU I shipped a full-stack insurance analytics platform on \textbf{React, Node.js, REST APIs}, Docker on EC2, with Stripe billing, RBAC, and row-level security across \textbf{6 clients} --- the closest cousin in my stack to a marketplace product. And at PwC I spent three years on a distributed \textbf{Azure backend} with event-driven processing over PostgreSQL and SQL Server. Multiple of your stack tracks line up here --- backend Python or frontend React+TypeScript would both be a natural fit.

What pulled me toward SeatGeek is the marketplace problem itself. Venue mapping, inventory tracking, event matching aren't generic CRUD problems --- they're irregular, weird-shaped constraints that need real custom craft. I got a taste of that shape at Amazon, building a console to track and query image/video evidence across fulfillment centers --- a different domain, but the same family of problem: inventory across distributed locations, filtering at scale, and custom views over operational data. That's the kind of work I want to keep building toward.

On the AI shift: I came up pre-AI --- bachelor's and PwC were core engineering (system design, data modeling, reliable backends). Then ML, deep learning, and big data through coursework. These days I use Cursor and GitHub Copilot daily, but I still verify trade-offs and understand the system before shipping production code. Fundamentals plus AI, not either alone.

I'd love the chance to bring that mix to SeatGeek --- on either the backend Python track or the React+TypeScript frontend. Thanks for considering my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
