%-------------------------
% Cover Letter - Cornerstone OnDemand Senior Software Engineer
% Author: Ajay Venkatesh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

May 4, 2026

\vspace{6pt}

Hiring Manager \\
Cornerstone OnDemand

\vspace{10pt}

Dear Hiring Manager,

My name is Ajay Venkatesh --- finishing my M.S. in Computer Engineering at NYU with several years of production software experience: a few at PwC in Bengaluru, a summer SDE internship at Amazon, and ongoing on-campus work at NYU's Novel AI Technologies. My focus has been on backend systems, cloud infrastructure, and increasingly the practical AI layer --- \textbf{RAG pipelines, agentic workflows,} and \textbf{LLM-powered features} built on top of real production systems.

The Cornerstone Senior Software Engineer posting is a strong match on a few axes. At Amazon I deployed a \textbf{Retrieval-Augmented Generation pipeline} with an \textbf{agentic workflow} for incident triage, implemented a \textbf{Model Context Protocol (MCP) server} that materially reduced AWS Athena query costs, and built an event-driven triage system on \textbf{AWS ECS Fargate, SQS, SNS} that decoupled distributed message processing and brought response latency down. At PwC I spent three years on a distributed backend on \textbf{Microsoft Azure} for a health platform, integrating \textbf{Microsoft CRM} with event-driven processing and fault-tolerant retries over \textbf{SQL Server}. At NYU's Novel AI Technologies I shipped a full-stack insurance analytics platform with \textbf{RBAC}, row-level security, Stripe billing, and end-to-end delivery to multiple paying clients --- the closest analog in my stack to enterprise SaaS.

What pulls me toward Cornerstone is the talent-platform problem itself. Learning paths and skill development are exactly the kind of personalized, behavior-driven workflows where modern AI actually adds value beyond keyword search. At Campus Mesh I built a \textbf{recommendation engine} (collaborative filtering + behavioral signals) that lifted engagement and retention --- small scale next to Cornerstone's enterprise customer base, but the same shape of problem.

On engineering rigor: my background is core enterprise software (system design, data modeling, reliable backends) plus ML, Deep Learning, and Big Data through graduate coursework and project work. I use Cursor and GitHub Copilot daily but verify trade-offs before shipping production code --- fundamentals plus AI, not either alone.

I'd welcome the chance to discuss how my backend + AI mix could contribute to Cornerstone's engineering team. Thanks for considering my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
