%-------------------------
% Cover Letter - Kai
% Author: Ajay Venkatesh
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 25, 2026

\vspace{6pt}

Hiring Manager \\
Kai

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh --- wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) with roughly four years of production experience: three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus data engineering at NYU's Novel AI Technologies. My focus has been \textbf{Python} and \textbf{PySpark} backends, distributed data pipelines, and AI/RAG infrastructure on AWS and Azure.

The Kai posting hits a few of my strongest threads. At NYU I built \textbf{ETL/ELT workflows} in Python, PySpark, and SQL, transforming NoSQL event data into PostgreSQL at \textbf{250K+ records}; at PwC I optimized \textbf{Apache Spark} batch ingestion across 100K-row feeds. On the AI infrastructure side, I shipped a \textbf{RAG pipeline} at Amazon with an LLM agent workflow plus a \textbf{Model Context Protocol (MCP) server} cutting Athena query cost \textbf{40\%}, and I built \textbf{CampusIQ} --- an LLM-powered assistant --- with embedding indexing, chunking, and \textbf{FAISS-based vector retrieval}. Combined, that maps to what your AI Platform team is building: data pipelines that feed into vector retrieval and LLM systems.

What pulled me toward Kai is the cybersecurity-meets-agentic-AI angle. Building data infrastructure for systems that contextualize, reason, and act at machine speed is a different problem from generic SaaS data work --- and the kind of stakes I want to grow into.

On the AI shift: I came up pre-AI --- bachelor's and PwC were core engineering (system design, data modeling, reliable backends). Then ML, deep learning, and big data through coursework. These days I use Cursor and GitHub Copilot daily, but I still verify trade-offs before shipping. Fundamentals plus AI, not either alone.

I'd love to bring that mix to Kai's AI Platform team. Thanks for considering my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
