%-------------------------
% Cover Letter - Omni Hotels & Resorts
% Author: Ajay Venkatesh
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.8in, bottom=0.8in, left=0.9in, right=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage{parskip}
\usepackage{microtype}

\setlength{\parskip}{6pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{flushleft}
\textbf{\large Ajay Venkatesh} \\
Brooklyn, NY \\
+1 516 585 9013 \\
\href{mailto:av3855@nyu.edu}{av3855@nyu.edu}
\end{flushleft}

\vspace{10pt}

April 24, 2026

\vspace{6pt}

Hiring Manager \\
Omni Hotels \& Resorts

\vspace{10pt}

Dear Hiring Manager,

My name's Ajay Venkatesh. I'm wrapping up my M.S. in Computer Engineering at NYU (3.9 GPA, May 2026) and have roughly four years of production software experience --- three at PwC in Bengaluru, a summer internship at Amazon, and ongoing on-campus data engineering work at NYU's Novel AI Technologies. Most of that time went into building distributed data pipelines, backend services, and cloud platforms on Azure and AWS.

The Omni posting reads like a checklist of work I've actually shipped. At PwC I spent three years on a distributed Azure backend --- SQL Server, event-driven ingestion, and parallel processing on 100K-row batch feeds --- close cousins of the Fabric pipeline work your team runs today. My NYU role pushed me deeper into ETL/ELT with Python, PySpark, and SQL, transforming NoSQL event data into PostgreSQL at around 250K records and powering QuickSight dashboards. And at Amazon, I shipped a RAG pipeline with an agentic workflow plus a Model Context Protocol server that cut Athena query cost and latency by 40\%, which lines up with the AI Agent and Fabric Data Agent direction you called out.

What drew me to Omni specifically is the modernization push you're on --- building a unified data platform for a 50+ property luxury hospitality business. Domain complexity like that is a different beast from generic SaaS data work, and it's exactly the kind of space I want to grow in over the next few years.

One quick note on the AI shift. I came up pre-AI --- my bachelor's and PwC years were all core engineering: system design, data modeling, reliable backends under real load. Then I went deeper through coursework in ML, deep learning, big data, and RAG. These days I use Cursor daily, but I don't trust it blindly --- I still verify trade-offs and understand the system before shipping production code. Strong fundamentals plus modern AI tools, not one or the other.

I'd welcome the chance to bring that mix to Omni's Fabric platform and help shape how your data story evolves. Thanks for taking the time to consider my application.

\vspace{12pt}

Sincerely, \\
Ajay Venkatesh

\end{document}
